### 2022-12-03 output/article.tex
feat: add article generation

\documentclass{article}
\usepackage{preamble}
\begin{document}
\maketitle
\newpage
\section{First section}

One shall regard the object in question with utmost interest:
\begin{equation}
\left( x + 1 \right) ^{\frac{\sin x }{2 } } \cdot \left( \arctan \sqrt {x ^{2 } + 1 } \right) ^{x - 2 } 
\end{equation}

We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
\begin{equation}
A \cdot \left( \arctan \sqrt {x ^{2 } + 1 } \right) ^{x - 2 } + \left( x + 1 \right) ^{\frac{\sin x }{2 } } \cdot C 
\end{equation}
Where:
\begin{itemize}
	\item $A = \left( x + 1 \right) ^{\frac{\sin x }{2 } } \cdot \left( \frac{\cos x \cdot 2 }{4 } \cdot \ln \left( x + 1 \right) + \frac{\sin x }{2 } \cdot \frac{1 }{x + 1 } \right) $
	\item $B = \frac{1 }{1 + \left( \sqrt {x ^{2 } + 1 } \right) ^{2 } } \cdot \frac{1 }{2 \cdot \sqrt {x ^{2 } + 1 } } \cdot 2 \cdot x $
	\item $C = \left( \arctan \sqrt {x ^{2 } + 1 } \right) ^{x - 2 } \cdot \left( \ln \arctan \sqrt {x ^{2 } + 1 } + \left( x - 2 \right) \cdot \frac{B }{\arctan \sqrt {x ^{2 } + 1 } } \right) $
\end{itemize}

We will take a closer look at this:
\begin{equation}
G + \left( F + \left( \arctan 1 \right) ^{-2 } \cdot \ln \arctan 1 + D + E \right) \cdot \frac{x ^{3 } }{6 } 
\end{equation}
Where:
\begin{itemize}
	\item $A = \left( \arctan 1 \right) ^{-2 } \cdot \ln \arctan 1 \cdot \ln \arctan 1 - \left( \arctan 1 \right) ^{-2 } \cdot 2 \cdot \frac{0.5 \cdot \arctan 1 }{\left( \arctan 1 \right) ^{2 } } $
	\item $B = \left( \arctan 1 \right) ^{-2 } \cdot \ln \arctan 1 \cdot \ln \arctan 1 - \left( \arctan 1 \right) ^{-2 } \cdot 2 \cdot \frac{0.5 \cdot \arctan 1 }{\left( \arctan 1 \right) ^{2 } } $
	\item $C = \frac{1 }{\arctan 1 } \cdot 0.5 + \frac{0.5 \cdot \arctan 1 }{\left( \arctan 1 \right) ^{2 } } + \frac{0.5 \cdot \arctan 1 }{\left( \arctan 1 \right) ^{2 } } $
	\item $D = \left( B \right) \cdot \ln \arctan 1 - \left( \arctan 1 \right) ^{-2 } \cdot \ln \arctan 1 \cdot 2 \cdot \frac{0.5 \cdot \arctan 1 }{\left( \arctan 1 \right) ^{2 } } $
	\item $E = \left( \arctan 1 \right) ^{-2 } \cdot \left( C \right) - \left( \arctan 1 \right) ^{-2 } \cdot \ln \arctan 1 \cdot 2 \cdot \frac{0.5 \cdot \arctan 1 }{\left( \arctan 1 \right) ^{2 } } $
	\item $F = \left( \arctan 1 \right) ^{-2 } \cdot \ln \arctan 1 - 1.5 \cdot \left( \arctan 1 \right) ^{-2 } + \left( \arctan 1 \right) ^{-2 } \cdot \ln \arctan 1 $
	\item $G = \left( \arctan 1 \right) ^{-2 } + \left( \arctan 1 \right) ^{-2 } \cdot \ln \arctan 1 \cdot x + \left( \left( \arctan 1 \right) ^{-2 } + A \right) \cdot \frac{x ^{2 } }{2 } $
\end{itemize}

\end{document}

### 2022-12-03 lib/article_builder/article_builder.cpp

@@ -1,0 +1,186 @@
+#include <stdlib.h>
+#include <time.h>
+
+#include "logger.h"
+
+#include "article_builder.h"
+
+static inline int rand_init(void) { srand(time(NULL)); return 1; }
+
+static int rand_initialized_ = rand_init();
+
+static inline size_t my_rand(void) {return (size_t) (rand() << 16 + rand()); }
+
+void article_ctor(article_builder *article)
+{
+    LOG_ASSERT(article, return);
+
+    *article = {.state = ARTC_NEW};
+    string_builder_ctor(&article->text, "\\documentclass{article}\n");
+}
+
+void article_use_starters(article_builder *article, const char *filename)
+{
+    LOG_ASSERT(article, return);
+    LOG_ASSERT(filename, return);
+
+    article->starters = read_file(filename);
+}
+
+void article_use_transitions(article_builder *article, const char *filename)
+{
+    LOG_ASSERT(article, return);
+    LOG_ASSERT(filename, return);
+
+    article->transitions = read_file(filename);
+}
+
+void article_use_placeholders(article_builder *article, const char *filename)
+{
+    LOG_ASSERT(article, return);
+    LOG_ASSERT(filename, return);
+
+    article->placeholders = read_file(filename);
+}
+
+void article_use_preamble(article_builder *article, const char *filename)
+{
+    LOG_ASSERT(article, return);
+    LOG_ASSERT(filename, return);
+    LOG_ASSERT(article->state == ARTC_NEW, return);
+
+    string_builder_append_format(&article->text, "\\usepackage{preamble}\n");
+    article->preamble = filename;
+}
+
+void article_dtor(article_builder *article)
+{
+    LOG_ASSERT(article, return);
+
+    string_builder_dtor(&article->text);
+    if (article->starters    .text != NULL) dispose_lines(&article->starters);
+    if (article->transitions .text != NULL) dispose_lines(&article->transitions);
+    if (article->placeholders.text != NULL) dispose_lines(&article->placeholders);
+
+    *article = {.state = ARTC_DELETED};
+}
+
+void article_add_title(article_builder *article, const char *title, const char* author)
+{
+    LOG_ASSERT(article, return);
+    LOG_ASSERT(title, return);
+    LOG_ASSERT(article->state == ARTC_NEW, return);
+
+    string_builder_append_format(&article->text, "\\title{%s}\n"
+                                                 "\\author{%s}\n",
+                                                 title, author);
[…]

### 2022-12-03 lib/article_builder/article_builder.h

@@ -1,0 +1,42 @@
+#ifndef ARTICLE_BUILDER
+#define ARTICLE_BUILDER
+
+#include "string_builder.h"
+#include "text_lines.h"
+
+enum article_state
+{
+    ARTC_NEW,
+    ARTC_TITLE,
+    ARTC_STARTED,
+    ARTC_ENDED,
+    ARTC_DELETED
+};
+
+struct article_builder
+{
+    article_state state;
+    TextLines starters;
+    TextLines transitions;
+    TextLines placeholders;
+    string_builder text;
+    const char* preamble;
+};
+
+void article_ctor(article_builder* article);
+void article_use_starters(article_builder* article, const char* filename);
+void article_use_transitions(article_builder* article, const char* filename);
+void article_use_placeholders(article_builder* article, const char* filename);
+void article_use_preamble(article_builder* article, const char* filename);
+void article_dtor(article_builder* article);
+void article_add_title(article_builder* article, const char* title, const char* author);
+void article_start(article_builder* article);
+void article_end(article_builder* article);
+void article_add_abstract(article_builder* article, const char* abstract);
+void article_add_section(article_builder* article, const char* title);
+void article_add_starter(article_builder* article);
+void article_add_transition(article_builder* article);
+void article_add_placeholder(article_builder* article);
+void article_build(article_builder* article, const char* output_dir);
+
+#endif

### 2022-12-03 lib/parser/ast.cpp

@@ -215,7 +215,7 @@ void print_node(const ast_node* root, string_builder * builder)
 
     string_builder_append_format(builder, "\\begin{equation}\n");
     print_subtree(root, labels, builder);
-    string_builder_append_format(builder, "\n\\end{equation}\n\n");
+    string_builder_append_format(builder, "\n\\end{equation}\n");
     if (has_labels(labels))
     {
         string_builder_append_format(builder, "Where:\n"

### 2022-12-03 src/main.cpp

@@ -7,6 +7,7 @@
 #include "lexer.h"
 #include "parser.h"
 #include "tree_math.h"
+#include "article_builder.h"
 
 int main()
 {
@@ -24,14 +25,27 @@ int main()
     abstract_syntax_tree* deriv = derivative(ast, "x");
     abstract_syntax_tree* maclaurin = maclaurin_series(ast, "x", 3);
 
-    string_builder builder = {};
-    string_builder_ctor(&builder);
+    article_builder article = {};
+    article_ctor(&article);
+    article_use_preamble(&article, "assets/preamble.sty");
+    article_use_starters(&article, "assets/starters.txt");
+    // article_add_title(&article, "Test article", "MeerkatBoss");
 
-    print_node(ast->root, &builder);
-    print_node(deriv->root, &builder);
-    print_node(maclaurin->root, &builder);
+    article_start(&article);
 
-    string_builder_write(&builder, STDOUT_FILENO);
+    // article_add_abstract(&article, "Wonderful article");
+    article_add_section(&article, "First section");
+
+    article_add_starter(&article);
+    print_node(ast->root, &article.text);
+    article_add_starter(&article);
+    print_node(deriv->root, &article.text);
+    article_add_starter(&article);
+    print_node(maclaurin->root, &article.text);
+
+    article_end(&article);
+
+    article_build(&article, "output");
 
     array_dtor(tokens);
     free(tokens);
@@ -39,6 +53,6 @@ int main()
     tree_dtor(ast);
     tree_dtor(deriv);
     tree_dtor(maclaurin);
-    string_builder_dtor(&builder);
+    article_dtor(&article);
     return 0;
 }

### 2022-12-03 output/article.tex
feat: add trash generation

@@
 \maketitle
+\begin{abstract}
+Wonderful article
+\end{abstract}
 \newpage
-\section{First section}
-
-One shall regard the object in question with utmost interest:
+\section{Derivative}
+Let us find the derivative of the following function:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x - 2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x + 1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+\sin x 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+Now the proof that the derivative of this function is equal to
+\begin{equation}
+\left( x + 1 \right) ^{\frac{\sin x }{2 } } \cdot \left( A \right) \cdot \left( \arctan \sqrt {x ^{2 } + 1 } \right) ^{x - 2 } + \left( x + 1 \right) ^{\frac{\sin x }{2 } } \cdot \left( \arctan \sqrt {x ^{2 } + 1 } \right) ^{x - 2 } \cdot \left( C \right)
+\end{equation}
+Where:
+\begin{itemize}
+	\item $A = \frac{\cos x \cdot 1 \cdot 2 - \sin x \cdot 0 }{2 ^{2 } } \cdot \ln \left( x + 1 \right) + \frac{\sin x }{2 } \cdot \frac{1 + 0 }{x + 1 } $
+	\item $B = \frac{1 }{1 + \left( \sqrt {x ^{2 } + 1 } \right) ^{2 } } \cdot \frac{1 }{2 \cdot \sqrt {x ^{2 } + 1 } } \cdot \left( 2 \cdot x ^{2 - 1 } \cdot 1 + 0 \right) $
+	\item $C = \left( 1 - 0 \right) \cdot \ln \arctan \sqrt {x ^{2 } + 1 } + \left( x - 2 \right) \cdot \frac{B }{\arctan \sqrt {x ^{2 } + 1 } } $
+\end{itemize}
+
+is left out for the reader to solve themselves.
+Unsurprisingly, if we simplify this we wil get
 \begin{equation}
@@
 
+\newpage
+\section{Taylor series}
+Let us find the Taylor series at $x = 0$ of the following function:
+\begin{equation}
+\left( x + 1 \right) ^{\frac{\sin x }{2 } } \cdot \left( \arctan \sqrt {x ^{2 } + 1 } \right) ^{x - 2 } 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x - 2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x + 1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
 We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+\sin x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x - 2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x - 2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x + 1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+\sin x 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x - 2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x + 1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+\sin x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x + 1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+4 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+\cos x 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+-\sin x \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x + 1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+\sin x 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x - 2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x - 2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x - 2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x - 2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x - 2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x + 1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+\sin x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x - 2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x - 2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x + 1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+\sin x 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x + 1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+4 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+\cos x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+-\sin x \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x + 1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+\sin x 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x - 2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x - 2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x + 1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+\sin x 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x + 1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+4 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+\cos x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+-\sin x \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x + 1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+\sin x 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x - 2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x + 1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+\sin x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x + 1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+4 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+\cos x 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+-\sin x \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x + 1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+16 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+0 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+4 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+\sin x 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x + 1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+4 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+\cos x 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+-\sin x \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x + 1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+\sin x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x + 1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+\sin x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x + 1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+4 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+\cos x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+-\sin x \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x + 1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+\sin x 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x + 1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+4 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+\cos x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+-\sin x \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x + 1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+\sin x 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x - 2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x - 2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x - 2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x - 2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x - 2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x - 2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x - 2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x - 2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x - 2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x - 2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x - 2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x - 2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x - 2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x - 2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x + 1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+\sin x 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x - 2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x - 2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x - 2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x - 2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x - 2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x + 1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+\sin x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x + 1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+4 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+\cos x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+-\sin x \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x + 1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+\sin x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x - 2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x - 2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x - 2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x - 2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x - 2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x + 1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+\sin x 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x + 1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+4 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+\cos x 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+-\sin x \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x + 1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+\sin x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x - 2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x - 2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x + 1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+\sin x 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x + 1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+4 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+\cos x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+-\sin x \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x + 1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+16 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+0 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+4 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+\sin x 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x + 1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+4 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+\cos x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+-\sin x \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x + 1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+\sin x 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x + 1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+\sin x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x + 1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+4 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+\cos x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+-\sin x \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x + 1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+\sin x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x + 1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+4 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+\cos x 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+-\sin x \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x + 1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+\sin x 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x - 2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x - 2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x - 2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x - 2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x - 2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x + 1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+\sin x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x + 1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+4 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+\cos x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+-\sin x \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x + 1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+\sin x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x - 2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x - 2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x + 1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+\sin x 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x + 1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+4 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+\cos x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+-\sin x \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x + 1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+16 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+0 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+4 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+\sin x 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x + 1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+4 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+\cos x 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+-\sin x \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x + 1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+\sin x 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x + 1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+\sin x 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x + 1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+4 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+\cos x 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+-\sin x \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x + 1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+\sin x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x + 1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+4 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+\cos x 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+-\sin x \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x + 1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+\sin x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x - 2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x - 2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x + 1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+\sin x 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x + 1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+4 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+\cos x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+-\sin x \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x + 1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+16 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+4 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+\sin x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x + 1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+4 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+\cos x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+-\sin x \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x + 1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+\sin x 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x + 1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+\sin x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x + 1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+4 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+\cos x 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+-\sin x \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x + 1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+\sin x 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x + 1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+4 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+\cos x 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+-\sin x \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x + 1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+\sin x 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x - 2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x + 1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x + 1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+\sin x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x + 1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+4 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+\cos x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+-\sin x \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x + 1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+4 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+\cos x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+-\sin x \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x + 1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+16 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+4 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+\sin x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x + 1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+16 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+4 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+\sin x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x + 1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+256 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+16 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+4 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+\cos x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+-\sin x \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x + 1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+4 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+\cos x 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+-\sin x \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x + 1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+16 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+4 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+\sin x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x + 1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+\sin x 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x + 1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+\sin x 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x + 1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+4 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+\cos x 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+-\sin x \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x + 1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+16 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+4 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+\sin x 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x + 1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+4 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+\cos x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+-\sin x \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x + 1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+\sin x 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x + 1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+4 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+\cos x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+-\sin x \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x + 1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+\sin x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x + 1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+\sin x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x + 1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+4 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+\cos x 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+-\sin x \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x + 1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+16 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+0 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+4 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+\sin x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x + 1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+4 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+\cos x 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+-\sin x \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x + 1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+\sin x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x + 1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+4 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+\cos x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+-\sin x \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x + 1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+\sin x 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x + 1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+\sin x 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x + 1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+4 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+\cos x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+-\sin x \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x + 1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+\sin x 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x + 1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+4 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+\cos x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+-\sin x \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x + 1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+16 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+0 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+4 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+\sin x 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x + 1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+4 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+\cos x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+-\sin x \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+x + 1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+\sin x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x + 1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+\sin x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x + 1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+4 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+\begin{equation}
+\cos x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+-\sin x \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x + 1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+\sin x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x + 1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+4 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+\cos x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+-\sin x \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x + 1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+\sin x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+Now the proof that the Taylor series of this function at $x = 0$ is equal to
+\begin{equation}
+B + \left( \left( \arctan 1 \right) ^{-2 } + A \right) \cdot \frac{x ^{2 } }{2 } + \left( G + H \right) \cdot \frac{x ^{3 } }{6 } 
+\end{equation}
+Where:
+\begin{itemize}
+	\item $A = \left( \arctan 1 \right) ^{-2 } \cdot \left( \ln \arctan 1 - 2 \cdot 0 \right) \cdot \left( \ln \arctan 1 - 2 \cdot 0 \right) - \left( \arctan 1 \right) ^{-2 } \cdot 2 \cdot \frac{0.5 \cdot \arctan 1 }{\left( \arctan 1 \right) ^{2 } } $
+	\item $B = 0 + \left( \arctan 1 \right) ^{-2 } \cdot \frac{x ^{0 } }{1 } + \left( \arctan 1 \right) ^{-2 } \cdot \left( \ln \arctan 1 - 2 \cdot 0 \right) \cdot \frac{x ^{1 } }{1 } $
+	\item $C = \left( \arctan 1 \right) ^{-2 } \cdot \left( \ln \arctan 1 - 2 \cdot 0 \right) \cdot \left( \ln \arctan 1 - 2 \cdot 0 \right) - \left( \arctan 1 \right) ^{-2 } \cdot 2 \cdot \frac{0.5 \cdot \arctan 1 }{\left( \arctan 1 \right) ^{2 } } $
+	\item $D = \left( \arctan 1 \right) ^{-2 } \cdot \left( \ln \arctan 1 - 2 \cdot 0 \right) \cdot 2 \cdot \frac{0.5 \cdot \arctan 1 }{\left( \arctan 1 \right) ^{2 } } $
+	\item $E = \frac{1 }{\arctan 1 } \cdot 0.5 + \frac{0.5 \cdot \arctan 1 }{\left( \arctan 1 \right) ^{2 } } + \frac{0.5 \cdot \arctan 1 }{\left( \arctan 1 \right) ^{2 } } - 2 \cdot 0 $
+	\item $F = \left( \arctan 1 \right) ^{-2 } \cdot \left( \ln \arctan 1 - 2 \cdot 0 \right) \cdot 2 \cdot \frac{0.5 \cdot \arctan 1 }{\left( \arctan 1 \right) ^{2 } } $
+	\item $G = \left( \arctan 1 \right) ^{-2 } \cdot \left( \ln \arctan 1 - 2 \cdot 0 \right) - 1.5 \cdot \left( \arctan 1 \right) ^{-2 } + \left( \arctan 1 \right) ^{-2 } \cdot \left( \ln \arctan 1 - 2 \cdot 0 \right) $
+	\item $H = \left( \arctan 1 \right) ^{-2 } \cdot \left( \ln \arctan 1 - 2 \cdot 0 \right) + \left( C \right) \cdot \left( \ln \arctan 1 - 2 \cdot 0 \right) - D + \left( \arctan 1 \right) ^{-2 } \cdot \left( E \right) - F $
+\end{itemize}
+
+shall be considered an amusing exercise for the reader.
+It can be easily proved, that if we simplify this we wil get
 \begin{equation}

### 2022-12-03 lib/article_builder/article_builder.cpp

@@ -9,7 +9,7 @@ static inline int rand_init(void) { srand(time(NULL)); return 1; }
 
 static int rand_initialized_ = rand_init();
 
-static inline size_t my_rand(void) {return (size_t) (rand() << 16 + rand()); }
+static inline size_t my_rand(void) {return ((size_t)rand() << 16) + (size_t)rand(); }
 
 void article_ctor(article_builder *article)
 {
@@ -142,11 +142,11 @@ void article_add_transition(article_builder *article)
 
     if (article->transitions.text == NULL)
     {
-        string_builder_append(&article->text, "Now look at this:\n");
+        string_builder_append(&article->text, "As you can see,");
         return;
     }
 
-    string_builder_append_format(&article->text, "%s\n",
+    string_builder_append_format(&article->text, "%s ",
                 article->transitions.lines[my_rand() % article->transitions.line_count].line);
 }
 
@@ -157,7 +157,7 @@ void article_add_placeholder(article_builder *article)
 
     if (article->placeholders.text == NULL)
     {
-        string_builder_append(&article->text, "Now look at this:\n");
+        string_builder_append(&article->text, "is easy to see.\n\n");
         return;
     }
 

### 2022-12-03 lib/math/tree_math.cpp

@@ -6,12 +6,12 @@
 #include "math_utils.h"
 #include "tree_math.h"
 
-static ast_node* get_differential(ast_node* node, var_name var);
+static ast_node* get_differential(ast_node* node, var_name var, article_builder* article, int no_print = 1);
 static void simplify_node(ast_node* node);
 static int is_const(ast_node* node, var_name var);
 static ast_node* evaluate_partially(ast_node* node, var_name var, double val);
 
-abstract_syntax_tree* derivative(abstract_syntax_tree * ast, const char * var)
+abstract_syntax_tree* derivative(abstract_syntax_tree * ast, const char * var, article_builder* article)
 {
     size_t var_id = 0;
     LOG_ASSERT_ERROR(
@@ -21,10 +21,22 @@ abstract_syntax_tree* derivative(abstract_syntax_tree * ast, const char * var)
     
     var_name v_name = *array_get_element(&ast->variables, var_id);
 
+    string_builder_append(&article->text, "Let us find the derivative of the following function:\n");
+    print_node(ast->root, &article->text);
+    
     abstract_syntax_tree* result = tree_copy(ast);
     
-    result->root = get_differential(ast->root, v_name);
+    result->root = get_differential(ast->root, v_name, article);
+
+    string_builder_append(&article->text, "\nNow the proof that the derivative of this function is equal to\n");
+    print_node(result->root, &article->text);
+    article_add_placeholder(article);
+
+    article_add_transition(article);
+    string_builder_append(&article->text, "if we simplify this we wil get\n");
     simplify(result);
+    print_node(result->root, &article->text);
+
 
     return result;
 }
@@ -52,17 +64,22 @@ static inline ast_node* COS (ast_node* right) { return make_unary_node(OP_COS, r
 static inline ast_node* SQRT(ast_node* right) { return make_unary_node(OP_SQRT, right);}
 static inline ast_node* LN  (ast_node* right) { return make_unary_node(OP_LN, right);  }
 
-#define D(x) get_differential(x, var)
+#define D(x) get_differential(x, var, article, print)
 
 static inline ast_node* CPY(ast_node* node) { return copy_subtree(node); }
 
-abstract_syntax_tree* maclaurin_series(abstract_syntax_tree * ast, const char * var, int pow)
+abstract_syntax_tree* maclaurin_series(abstract_syntax_tree * ast, const char * var, int pow, article_builder* article)
 {
     size_t var_id = 0;
[…]

### 2022-12-03 lib/math/tree_math.h

@@ -1,14 +1,17 @@
 #ifndef TREE_MATH_H
 #define TREE_MATH_H
 
+#include <stddef.h>
+
+#include "article_builder.h"
+
 #include "ast.h"
 
-
 // TODO: make docs
-abstract_syntax_tree* derivative(abstract_syntax_tree* ast, const char* var);
+abstract_syntax_tree* derivative(abstract_syntax_tree* ast, const char* var, article_builder* article);
 
 void simplify(abstract_syntax_tree* ast);
 
-abstract_syntax_tree* maclaurin_series(abstract_syntax_tree* ast, const char* var, int pow);
+abstract_syntax_tree* maclaurin_series(abstract_syntax_tree* ast, const char* var, int pow, article_builder* article);
 
 #endif

### 2022-12-03 src/main.cpp

@@ -19,29 +19,26 @@ int main()
         .settings_mask = LGS_KEEP_OPEN | LGS_USE_ESCAPE
     }); // TODO: can this be in default logger?
 
+
     dynamic_array(token)* tokens = parse_tokens("(x + 1)^{\\frac{\\sin x}{2}} \\cdot (\\arctan \\sqrt{x^2 + 1})^{x - 2}");
     // dynamic_array(token)* tokens = parse_tokens("\\frac{1}{x + 1}");
     abstract_syntax_tree* ast = build_tree(tokens);
-    abstract_syntax_tree* deriv = derivative(ast, "x");
-    abstract_syntax_tree* maclaurin = maclaurin_series(ast, "x", 3);
 
     article_builder article = {};
     article_ctor(&article);
     article_use_preamble(&article, "assets/preamble.sty");
     article_use_starters(&article, "assets/starters.txt");
-    // article_add_title(&article, "Test article", "MeerkatBoss");
+    article_use_transitions(&article, "assets/transitions.txt");
+    article_use_placeholders(&article, "assets/placeholders.txt");
 
     article_start(&article);
+    article_add_abstract(&article, "Wonderful article");
 
-    // article_add_abstract(&article, "Wonderful article");
-    article_add_section(&article, "First section");
+    article_add_section(&article, "Derivative");
+    abstract_syntax_tree* deriv = derivative(ast, "x", &article);
 
-    article_add_starter(&article);
-    print_node(ast->root, &article.text);
-    article_add_starter(&article);
-    print_node(deriv->root, &article.text);
-    article_add_starter(&article);
-    print_node(maclaurin->root, &article.text);
+    article_add_section(&article, "Taylor series");
+    abstract_syntax_tree* maclaurin = maclaurin_series(ast, "x", 3, &article);
 
     article_end(&article);
 

### 2022-12-04 output/article.tex
feat: add node plotting

@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 \end{equation}
-Unsurprisingly, the derivative of this is equal to
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
+We shall ponder the following:
 \begin{equation}
@@
 \end{equation}
-It can be easily proved, that the derivative of this is equal to
+As you can see, the derivative of this is equal to
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 \end{equation}
-It is now obvious, that the derivative of this is equal to
+Obviously, the derivative of this is equal to
 \begin{equation}
@@
 
-is left out for the reader to solve themselves.
-Unsurprisingly, if we simplify this we wil get
+has a truly wondrous solution, which is sadly too massive to be shown here.
+It can be easily proved, that if we simplify this we wil get
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 \end{equation}
-As you can see, the derivative of this is equal to
+Unsurprisingly, the derivative of this is equal to
 \begin{equation}
@@
 
-The following is worth a closer look:
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 \end{equation}
-Unsurprisingly, the derivative of this is equal to
+It can be easily proved, that the derivative of this is equal to
 \begin{equation}
@@
 
-Let us take a look at this:
+We are going to study the following:
 \begin{equation}
@@
 \end{equation}
-Trivially, the derivative of this is equal to
+It can be easily proved, that the derivative of this is equal to
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 \end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+As you can see, the derivative of this is equal to
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 \end{equation}
-As you can see, the derivative of this is equal to
+It can be easily proved, that the derivative of this is equal to
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
+We shall ponder the following:
 \begin{equation}
@@
 \end{equation}
-Clearly, the derivative of this is equal to
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 \end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 \end{equation}
-Clearly, the derivative of this is equal to
+It can be easily proved, that the derivative of this is equal to
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
+Let us take a look at this:
 \begin{equation}
@@
 \end{equation}
-It can be easily proved, that the derivative of this is equal to
+Clearly, the derivative of this is equal to
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 \end{equation}
-Unsurprisingly, the derivative of this is equal to
+It is now obvious, that the derivative of this is equal to
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+Let us take a look at this:
 \begin{equation}
@@
 \end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 \end{equation}
-Unsurprisingly, the derivative of this is equal to
+As you can see, the derivative of this is equal to
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+The following is worth a closer look:
 \begin{equation}
@@
 \end{equation}
-Obviously, the derivative of this is equal to
+As you can see, the derivative of this is equal to
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
 \begin{equation}
@@
 \end{equation}
-It is now obvious, that the derivative of this is equal to
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 \end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+Trivially, the derivative of this is equal to
 \begin{equation}
@@
 \end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 \end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+It can be easily proved, that the derivative of this is equal to
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 \end{equation}
-Trivially, the derivative of this is equal to
+As you can see, the derivative of this is equal to
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 \end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+It is now obvious, that the derivative of this is equal to
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 \end{equation}
-Trivially, the derivative of this is equal to
+It is now obvious, that the derivative of this is equal to
 \begin{equation}
@@
 \end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 \end{equation}
-Trivially, the derivative of this is equal to
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 \end{equation}
-Obviously, the derivative of this is equal to
+Unsurprisingly, the derivative of this is equal to
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 \end{equation}
-It is now obvious, that the derivative of this is equal to
+Clearly, the derivative of this is equal to
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 \end{equation}
-Obviously, the derivative of this is equal to
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 
-The following is worth a closer look:
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 \end{equation}
-It can be easily proved, that the derivative of this is equal to
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 \end{equation}
-It can be easily proved, that the derivative of this is equal to
+Unsurprisingly, the derivative of this is equal to
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 \end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+Obviously, the derivative of this is equal to
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
 \begin{equation}
@@
 \end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-We are going to study the following:
+Consider the following:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 \end{equation}
-Clearly, the derivative of this is equal to
+It is now obvious, that the derivative of this is equal to
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
+The following is worth a closer look:
 \begin{equation}
@@
 
-We are going to study the following:
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 \end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
+We will take a closer look at this:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 \end{equation}
-Obviously, the derivative of this is equal to
+It is now obvious, that the derivative of this is equal to
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 \end{equation}
-It is now obvious, that the derivative of this is equal to
+Unsurprisingly, the derivative of this is equal to
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 \end{equation}
-As you can see, the derivative of this is equal to
+Clearly, the derivative of this is equal to
 \begin{equation}
@@
 
-The following is worth a closer look:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 \end{equation}
-It is now obvious, that the derivative of this is equal to
+As you can see, the derivative of this is equal to
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-We are going to study the following:
+The following is worth a closer look:
 \begin{equation}
@@
 
-Let us take a look at this:
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 \end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 \end{equation}
-Unsurprisingly, the derivative of this is equal to
+Clearly, the derivative of this is equal to
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 \end{equation}
-It is now obvious, that the derivative of this is equal to
+Trivially, the derivative of this is equal to
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-We are going to study the following:
+Let us take a look at this:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 \end{equation}
-As you can see, the derivative of this is equal to
+It is now obvious, that the derivative of this is equal to
 \begin{equation}
@@
 
-Consider the following:
+The following is worth a closer look:
 \begin{equation}
@@
 \end{equation}
-Clearly, the derivative of this is equal to
+Trivially, the derivative of this is equal to
 \begin{equation}
@@
 \end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-0 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+0 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 \end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 
-Let us take a look at this:
+Consider the following:
 \begin{equation}
@@
 \end{equation}
-It can be easily proved, that the derivative of this is equal to
+It is now obvious, that the derivative of this is equal to
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 \end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-Let us take a look at this:
+We shall ponder the following:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
 \begin{equation}
@@
 \end{equation}
-Trivially, the derivative of this is equal to
+Unsurprisingly, the derivative of this is equal to
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 \end{equation}
-It can be easily proved, that the derivative of this is equal to
+Obviously, the derivative of this is equal to
 \begin{equation}
@@
 
-We shall ponder the following:
+We will take a closer look at this:
 \begin{equation}
@@
 
-The following is worth a closer look:
+We will take a closer look at this:
 \begin{equation}
@@
 \end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 \end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-We are going to study the following:
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 \end{equation}
-As you can see, the derivative of this is equal to
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 \end{equation}
-As you can see, the derivative of this is equal to
+Trivially, the derivative of this is equal to
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 \end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+Clearly, the derivative of this is equal to
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 \end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 \end{equation}
-Clearly, the derivative of this is equal to
+Obviously, the derivative of this is equal to
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 \end{equation}
-It is now obvious, that the derivative of this is equal to
+It can be easily proved, that the derivative of this is equal to
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 \end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+Unsurprisingly, the derivative of this is equal to
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 \end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 \end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 \end{equation}
-Obviously, the derivative of this is equal to
+It can be easily proved, that the derivative of this is equal to
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 \end{equation}
-Unsurprisingly, the derivative of this is equal to
+Obviously, the derivative of this is equal to
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 \end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 \end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 \end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 \end{equation}
-It can be easily proved, that the derivative of this is equal to
+Trivially, the derivative of this is equal to
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 \end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 \end{equation}
-Trivially, the derivative of this is equal to
+Clearly, the derivative of this is equal to
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 \end{equation}
-Clearly, the derivative of this is equal to
+As you can see, the derivative of this is equal to
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 \end{equation}
-Trivially, the derivative of this is equal to
+Obviously, the derivative of this is equal to
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 \end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
 \begin{equation}
@@
 
-We shall ponder the following:
+We are going to study the following:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 \end{equation}
-As you can see, the derivative of this is equal to
+Obviously, the derivative of this is equal to
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 \end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-Let us take a look at this:
+The following is worth a closer look:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 \end{equation}
-Clearly, the derivative of this is equal to
+Unsurprisingly, the derivative of this is equal to
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 \end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 \end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 
-We are going to study the following:
+We shall ponder the following:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 
-The following is worth a closer look:
+Consider the following:
 \begin{equation}
@@
 \end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 
-Consider the following:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-Consider the following:
+We shall ponder the following:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 \end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
 \begin{equation}
@@
 
-We shall ponder the following:
+The following is worth a closer look:
 \begin{equation}
@@
 \end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-0 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+0 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 \end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 \end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 
-We will take a closer look at this:
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-Consider the following:
+We are going to study the following:
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 \end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+We will take a closer look at this:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-We shall ponder the following:
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 \end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-We will take a closer look at this:
+Let us take a look at this:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 \end{equation}
-Obviously, the derivative of this is equal to
+Trivially, the derivative of this is equal to
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 \end{equation}
-Unsurprisingly, the derivative of this is equal to
+Trivially, the derivative of this is equal to
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
 \begin{equation}
@@
 \end{equation}
-Obviously, the derivative of this is equal to
+Clearly, the derivative of this is equal to
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 
-We will take a closer look at this:
+Consider the following:
 \begin{equation}
@@
 \end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 \end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 
-We will take a closer look at this:
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
 \begin{equation}
@@
 
-We will take a closer look at this:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
 \begin{equation}
@@
 \end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 \end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-0 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+0 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 \end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 \end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-Consider the following:
+Let us take a look at this:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
+Consider the following:
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-We will take a closer look at this:
+We shall ponder the following:
 \begin{equation}
@@
 \end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
 \begin{equation}
@@
 \end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-The following is worth a closer look:
+We shall ponder the following:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-The following is worth a closer look:
+We are going to study the following:
 \begin{equation}
@@
 \end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 \end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 \end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 \end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
 \begin{equation}
@@
 
-We are going to study the following:
+We will take a closer look at this:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 \end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+We are going to study the following:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
+We will take a closer look at this:
 \begin{equation}
@@
 \end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 \end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-Consider the following:
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 \end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 \end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 \end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 \end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 \end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 \end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 \end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 \end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 \end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 \end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 \end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 
-We will take a closer look at this:
+We are going to study the following:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
+Let us take a look at this:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 \end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 \end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 \end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 \end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 \end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
+The following is worth a closer look:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 \end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-We shall ponder the following:
+Consider the following:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 \end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 \end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-0 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+0 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 \end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 \end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-We are going to study the following:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 \end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 \end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-Let us take a look at this:
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-0 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+The object of our ultimate interest is the following:
+\begin{equation}
+0 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 \end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
 \begin{equation}
@@
 
-We shall ponder the following:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 \end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-The following is worth a closer look:
+Let us take a look at this:
 \begin{equation}
@@
 \end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attentions to this gem of mathematical wonder:
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-Consider the following:
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 \end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-shall be considered an amusing exercise for the reader.
-It can be easily proved, that if we simplify this we wil get
+has a truly wondrous solution, which is sadly too massive to be shown here.
+Unsurprisingly, if we simplify this we wil get
 \begin{equation}

### 2022-12-04 lib/parser/ast.cpp

@@ -176,6 +176,50 @@ tree_iterator tree_end(abstract_syntax_tree* tree)
     return node;
 }
 
+void plot_node(const ast_node *node, FILE *output)
+{
+    #define PLOT_INFIX(op) do\
+        {\
+            fputc('(', output); plot_node(node->left, output);\
+            fputs(")" #op "(", output); plot_node(node->right, output); fputc(')', output);\
+        } while(0)
+    #define PLOT_UNARY(op) do\
+        {\
+            fputs(#op "(", output); plot_node(node->right, output); fputc(')', output);\
+        } while(0)
+    #define PLOT_COMPOUND(op, plot) do\
+        {\
+            fputs("(" #op "(", output); plot; fputs("))", output);\
+        } while(0)
+    
+    if (is_num(node)) { fprintf(output, "%g", get_num(node)); return; }
+    if (is_var(node)) { fprintf(output, "%s", get_var(node)); return; }
+
+    switch(get_op(node))
+    {
+    case OP_ADD:    PLOT_INFIX(+);                          break;
+    case OP_SUB:    PLOT_INFIX(-);                          break;
+    case OP_MUL:    PLOT_INFIX(*);                          break;
+    case OP_DIV:    PLOT_INFIX(/);                          break;
+    case OP_NEG:    PLOT_UNARY(-);                          break;
+    case OP_LN:     PLOT_UNARY(log);                        break;
+    case OP_SQRT:   PLOT_UNARY(sqrt);                       break;
+    case OP_SIN:    PLOT_UNARY(sin);                        break;
+    case OP_COS:    PLOT_UNARY(cos);                        break;
+    case OP_TAN:    PLOT_UNARY(tan);                        break;
+    case OP_COT:    PLOT_COMPOUND(1/, PLOT_UNARY(tan));     break;
+    case OP_ARCSIN: PLOT_UNARY(asin);                       break;
+    case OP_ARCCOS: PLOT_COMPOUND(pi/2-, PLOT_UNARY(asin)); break;
+    case OP_ARCTAN: PLOT_UNARY(atan);                       break;
+    case OP_ARCCOT: PLOT_COMPOUND(pi/2, PLOT_UNARY(atan));  break;
+    case OP_POW:    PLOT_INFIX(**);                         break;
+    }
+
+    #undef PLOT_INFIX
+    #undef PLOT_UNARY
+    #undef PLOT_COMPOUND
+}
+
 static const int MAX_LABELS = 'Z'-'A'+1;
 
 

### 2022-12-04 lib/parser/ast.h

@@ -241,4 +241,12 @@ tree_iterator tree_end(abstract_syntax_tree* tree);
  */
 void print_node(const ast_node* node, string_builder* builder);
 
+/**
+ * @brief Output node such that gnuplot would understand it
+ * 
+ * @param[in] node Plotted node
+ * @param[in] output Output stream
+ */
+void plot_node(const ast_node* node, FILE* output);
+
 #endif

### 2022-12-04 src/main.cpp

@@ -47,6 +47,9 @@ int main()
     array_dtor(tokens);
     free(tokens);
 
+    plot_node(ast->root, stdout);
+    putc('\n', stdout);
+
     tree_dtor(ast);
     tree_dtor(deriv);
     tree_dtor(maclaurin);

### 2022-12-04 output/article.tex
feat: generalize maclaurin series to taylor series

@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-x + 1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x + 1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 \section{Taylor series}
-Let us find the Taylor series at $x = 0$ of the following function:
+Let us find the Taylor series at $x = 5$ of the following function:
 \begin{equation}
@@
 
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x - 2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x + 1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+\sin x 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x - 2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x - 2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x + 1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+\sin x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x - 2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x + 1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+\sin x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
 The following is worth a closer look:
 \begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x - 2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x + 1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
+x + 1 
 \end{equation}
@@
 \begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+1 + 0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+4 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+\cos x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+-\sin x \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x + 1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x - 2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x - 2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x + 1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-\sin x 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x - 2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x + 1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-\sin x 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x + 1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-4 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-\cos x 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
--\sin x \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x + 1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-\sin x 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x - 2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x - 2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x - 2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x - 2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x - 2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x + 1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-\sin x 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x - 2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x - 2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x + 1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-\sin x 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x + 1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-4 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-\cos x 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
--\sin x \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x + 1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-\sin x 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x - 2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x - 2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x + 1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-\sin x 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x + 1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-4 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-\cos x 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
--\sin x \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x + 1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-\sin x 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x - 2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x + 1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-\sin x 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x + 1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-4 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-\cos x 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
--\sin x \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x + 1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-16 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-0 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-4 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-\sin x 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x + 1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-4 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-\cos x 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
--\sin x \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x + 1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-\sin x 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x + 1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-\sin x 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x + 1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-4 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-\cos x 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
--\sin x \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x + 1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-\sin x 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x + 1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-4 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-\cos x 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
--\sin x \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x + 1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-\sin x 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x - 2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x - 2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x - 2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x - 2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x - 2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x - 2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x - 2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x - 2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x - 2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x - 2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x - 2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x - 2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x - 2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x - 2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x + 1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-\sin x 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x - 2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x - 2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x - 2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x - 2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x - 2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x + 1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-\sin x 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x + 1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-4 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-\cos x 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
--\sin x \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x + 1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-\sin x 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x - 2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x - 2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x - 2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x - 2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x - 2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x + 1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-\sin x 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x + 1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-4 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-\cos x 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
--\sin x \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x + 1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-\sin x 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x - 2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x - 2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x + 1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-\sin x 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x + 1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-4 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-\cos x 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
--\sin x \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x + 1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-16 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-0 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-4 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-\sin x 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x + 1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-4 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-\cos x 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
--\sin x \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x + 1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-\sin x 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x + 1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-\sin x 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x + 1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-4 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-\cos x 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
--\sin x \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x + 1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-\sin x 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x + 1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-4 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-\cos x 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
--\sin x \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x + 1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-\sin x 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x - 2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x - 2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x - 2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x - 2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x - 2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x + 1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-\sin x 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x + 1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-4 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-\cos x 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
--\sin x \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x + 1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-\sin x 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x - 2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x - 2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x + 1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-\sin x 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x + 1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-4 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-\cos x 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
--\sin x \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x + 1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-16 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-0 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-4 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-\sin x 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x + 1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-4 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-\cos x 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
--\sin x \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x + 1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-\sin x 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x + 1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-\sin x 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x + 1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-4 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-\cos x 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
--\sin x \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x + 1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-\sin x 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x + 1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-4 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-\cos x 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
--\sin x \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x + 1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-\sin x 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x - 2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x - 2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x + 1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-\sin x 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x + 1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-4 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-\cos x 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
--\sin x \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x + 1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-16 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-4 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-\sin x 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x + 1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-4 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-\cos x 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
--\sin x \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x + 1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-\sin x 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x + 1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-\sin x 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x + 1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-4 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-\cos x 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
--\sin x \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x + 1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-\sin x 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x + 1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-4 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-\cos x 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
--\sin x \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x + 1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-\sin x 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x - 2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x + 1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x + 1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-\sin x 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x + 1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-4 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-\cos x 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
--\sin x \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x + 1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-4 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-\cos x 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
--\sin x \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x + 1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-16 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-4 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-\sin x 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x + 1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-16 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-4 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-\sin x 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x + 1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-256 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-16 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-4 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-\cos x 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
--\sin x \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x + 1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-4 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-\cos x 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
--\sin x \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x + 1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-16 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-4 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-\sin x 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x + 1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-\sin x 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x + 1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-\sin x 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x + 1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-4 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-\cos x 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
--\sin x \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x + 1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-16 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-4 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-\sin x 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x + 1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-4 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-\cos x 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
--\sin x \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x + 1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-\sin x 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x + 1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-4 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-\cos x 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
--\sin x \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x + 1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-\sin x 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x + 1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-\sin x 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x + 1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-4 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-\cos x 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
--\sin x \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x + 1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-16 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-0 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-4 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-\sin x 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x + 1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-4 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-\cos x 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
--\sin x \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x + 1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-\sin x 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x + 1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-4 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-\cos x 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
--\sin x \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x + 1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-\sin x 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x + 1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-\sin x 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x + 1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-4 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-\cos x 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
--\sin x \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x + 1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-\sin x 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x + 1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-4 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-\cos x 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
--\sin x \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x + 1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-16 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-0 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-4 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-\sin x 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x + 1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-4 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-\cos x 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
--\sin x \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x + 1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-\sin x 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x + 1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-\sin x 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x + 1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-4 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-\cos x 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
--\sin x \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x + 1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-\sin x 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x + 1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-4 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-\cos x 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
--\sin x \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x + 1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-\sin x 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-Now the proof that the Taylor series of this function at $x = 0$ is equal to
-\begin{equation}
-B + \left( \left( \arctan 1 \right) ^{-2 } + A \right) \cdot \frac{x ^{2 } }{2 } + \left( G + H \right) \cdot \frac{x ^{3 } }{6 } 
+Now the proof that the Taylor series of this function at $x = 5$ is equal to
+\begin{equation}
+0 + 6 ^{\frac{\sin 5 }{2 } } \cdot \left( \arctan \sqrt {26 } \right) ^{3 } \cdot \frac{\left( x - 5 \right) ^{0 } }{1 } + \left( B + 6 ^{\frac{\sin 5 }{2 } } \cdot \left( \arctan \sqrt {26 } \right) ^{3 } \cdot \left( A \right) \right) \cdot \frac{\left( x - 5 \right) ^{1 } }{1 }
 \end{equation}
@@
 \begin{itemize}
-	\item $A = \left( \arctan 1 \right) ^{-2 } \cdot \left( \ln \arctan 1 - 2 \cdot 0 \right) \cdot \left( \ln \arctan 1 - 2 \cdot 0 \right) - \left( \arctan 1 \right) ^{-2 } \cdot 2 \cdot \frac{0.5 \cdot \arctan 1 }{\left( \arctan 1 \right) ^{2 } } $
-	\item $B = 0 + \left( \arctan 1 \right) ^{-2 } \cdot \frac{x ^{0 } }{1 } + \left( \arctan 1 \right) ^{-2 } \cdot \left( \ln \arctan 1 - 2 \cdot 0 \right) \cdot \frac{x ^{1 } }{1 } $
-	\item $C = \left( \arctan 1 \right) ^{-2 } \cdot \left( \ln \arctan 1 - 2 \cdot 0 \right) \cdot \left( \ln \arctan 1 - 2 \cdot 0 \right) - \left( \arctan 1 \right) ^{-2 } \cdot 2 \cdot \frac{0.5 \cdot \arctan 1 }{\left( \arctan 1 \right) ^{2 } } $
-	\item $D = \left( \arctan 1 \right) ^{-2 } \cdot \left( \ln \arctan 1 - 2 \cdot 0 \right) \cdot 2 \cdot \frac{0.5 \cdot \arctan 1 }{\left( \arctan 1 \right) ^{2 } } $
-	\item $E = \frac{1 }{\arctan 1 } \cdot 0.5 + \frac{0.5 \cdot \arctan 1 }{\left( \arctan 1 \right) ^{2 } } + \frac{0.5 \cdot \arctan 1 }{\left( \arctan 1 \right) ^{2 } } - 2 \cdot 0 $
-	\item $F = \left( \arctan 1 \right) ^{-2 } \cdot \left( \ln \arctan 1 - 2 \cdot 0 \right) \cdot 2 \cdot \frac{0.5 \cdot \arctan 1 }{\left( \arctan 1 \right) ^{2 } } $
-	\item $G = \left( \arctan 1 \right) ^{-2 } \cdot \left( \ln \arctan 1 - 2 \cdot 0 \right) - 1.5 \cdot \left( \arctan 1 \right) ^{-2 } + \left( \arctan 1 \right) ^{-2 } \cdot \left( \ln \arctan 1 - 2 \cdot 0 \right) $
-	\item $H = \left( \arctan 1 \right) ^{-2 } \cdot \left( \ln \arctan 1 - 2 \cdot 0 \right) + \left( C \right) \cdot \left( \ln \arctan 1 - 2 \cdot 0 \right) - D + \left( \arctan 1 \right) ^{-2 } \cdot \left( E \right) - F $
+	\item $A = \ln \arctan \sqrt {26 } + 3 \cdot \frac{\frac{1 }{1 + \left( \sqrt {26 } \right) ^{2 } } \cdot \frac{1 }{2 \cdot \sqrt {26 } } \cdot 10 }{\arctan \sqrt {26 } } $
+	\item $B = 6 ^{\frac{\sin 5 }{2 } } \cdot \left( \frac{\cos 5 \cdot 2 }{4 } \cdot \ln 6 + \frac{\sin 5 }{2 } \cdot 0.166667 \right) \cdot \left( \arctan \sqrt {26 } \right) ^{3 } $
 \end{itemize}
 
-has a truly wondrous solution, which is sadly too massive to be shown here.
-Unsurprisingly, if we simplify this we wil get
-\begin{equation}
-G + \left( F + \left( \arctan 1 \right) ^{-2 } \cdot \ln \arctan 1 + D + E \right) \cdot \frac{x ^{3 } }{6 } 
+is too trivial to be shown here.
+It is now obvious, that if we simplify this we wil get
+\begin{equation}
+6 ^{\frac{\sin 5 }{2 } } \cdot \left( \arctan \sqrt {26 } \right) ^{3 } + \left( B + 6 ^{\frac{\sin 5 }{2 } } \cdot \left( \arctan \sqrt {26 } \right) ^{3 } \cdot \left( A \right) \right) \cdot \left( x - 5 \right)
 \end{equation}
@@
 \begin{itemize}
-	\item $A = \left( \arctan 1 \right) ^{-2 } \cdot \ln \arctan 1 \cdot \ln \arctan 1 - \left( \arctan 1 \right) ^{-2 } \cdot 2 \cdot \frac{0.5 \cdot \arctan 1 }{\left( \arctan 1 \right) ^{2 } } $
-	\item $B = \left( \arctan 1 \right) ^{-2 } \cdot \ln \arctan 1 \cdot \ln \arctan 1 - \left( \arctan 1 \right) ^{-2 } \cdot 2 \cdot \frac{0.5 \cdot \arctan 1 }{\left( \arctan 1 \right) ^{2 } } $
-	\item $C = \frac{1 }{\arctan 1 } \cdot 0.5 + \frac{0.5 \cdot \arctan 1 }{\left( \arctan 1 \right) ^{2 } } + \frac{0.5 \cdot \arctan 1 }{\left( \arctan 1 \right) ^{2 } } $
-	\item $D = \left( B \right) \cdot \ln \arctan 1 - \left( \arctan 1 \right) ^{-2 } \cdot \ln \arctan 1 \cdot 2 \cdot \frac{0.5 \cdot \arctan 1 }{\left( \arctan 1 \right) ^{2 } } $
-	\item $E = \left( \arctan 1 \right) ^{-2 } \cdot \left( C \right) - \left( \arctan 1 \right) ^{-2 } \cdot \ln \arctan 1 \cdot 2 \cdot \frac{0.5 \cdot \arctan 1 }{\left( \arctan 1 \right) ^{2 } } $
-	\item $F = \left( \arctan 1 \right) ^{-2 } \cdot \ln \arctan 1 - 1.5 \cdot \left( \arctan 1 \right) ^{-2 } + \left( \arctan 1 \right) ^{-2 } \cdot \ln \arctan 1 $
-	\item $G = \left( \arctan 1 \right) ^{-2 } + \left( \arctan 1 \right) ^{-2 } \cdot \ln \arctan 1 \cdot x + \left( \left( \arctan 1 \right) ^{-2 } + A \right) \cdot \frac{x ^{2 } }{2 } $
+	\item $A = \ln \arctan \sqrt {26 } + 3 \cdot \frac{\frac{1 }{1 + \left( \sqrt {26 } \right) ^{2 } } \cdot \frac{1 }{2 \cdot \sqrt {26 } } \cdot 10 }{\arctan \sqrt {26 } } $
+	\item $B = 6 ^{\frac{\sin 5 }{2 } } \cdot \left( \frac{\cos 5 \cdot 2 }{4 } \cdot \ln 6 + \frac{\sin 5 }{2 } \cdot 0.166667 \right) \cdot \left( \arctan \sqrt {26 } \right) ^{3 } $
 \end{itemize}

### 2022-12-04 lib/math/tree_math.cpp

@@ -68,7 +68,12 @@ static inline ast_node* LN  (ast_node* right) { return make_unary_node(OP_LN, ri
 
 static inline ast_node* CPY(ast_node* node) { return copy_subtree(node); }
 
-abstract_syntax_tree* maclaurin_series(abstract_syntax_tree * ast, const char * var, int pow, article_builder* article)
+abstract_syntax_tree* taylor_series(
+                            abstract_syntax_tree * ast,
+                            double point,
+                            const char * var,
+                            int pow,
+                            article_builder* article)
 {
     size_t var_id = 0;
     LOG_ASSERT_ERROR(
@@ -78,7 +83,7 @@ abstract_syntax_tree* maclaurin_series(abstract_syntax_tree * ast, const char * 
 
     string_builder_append_format(&article->text, "Let us find the Taylor series"
                                                  " at $%s = %g$ of the following function:\n",
-                                                 var, 0.0);
+                                                 var, point);
     print_node(ast->root, &article->text);
 
     abstract_syntax_tree* result = tree_copy(ast);
@@ -89,7 +94,7 @@ abstract_syntax_tree* maclaurin_series(abstract_syntax_tree * ast, const char * 
     ast_node* cur = CPY(ast->root);
     for (int i = 0; i <= pow; i++)
     {
-        ast_node* at_zero = evaluate_partially(cur, v_name, 0);
+        ast_node* at_zero = evaluate_partially(cur, v_name, point);
         simplify_node(at_zero);
         result->root =
             ADD(
@@ -97,7 +102,9 @@ abstract_syntax_tree* maclaurin_series(abstract_syntax_tree * ast, const char * 
                 MUL(
                     at_zero,
                     FRAC(
-                        POW(VAR(v_name), NUM(i)),
+                        POW(
+                            SUB(VAR(v_name), NUM(point)),
+                            NUM(i)),
                         NUM(factorial(i))
                     )
                 )
@@ -110,7 +117,7 @@ abstract_syntax_tree* maclaurin_series(abstract_syntax_tree * ast, const char * 
     delete_subtree(cur);
 
     string_builder_append_format(&article->text, "\nNow the proof that the Taylor series of this function"
-                                                 " at $%s = %g$ is equal to\n", var, 0.0);
+                                                 " at $%s = %g$ is equal to\n", var, point);
     print_node(result->root, &article->text);
     article_add_placeholder(article);
 

### 2022-12-04 lib/math/tree_math.h

@@ -12,6 +12,11 @@ abstract_syntax_tree* derivative(abstract_syntax_tree* ast, const char* var, art
 
 void simplify(abstract_syntax_tree* ast);
 
-abstract_syntax_tree* maclaurin_series(abstract_syntax_tree* ast, const char* var, int pow, article_builder* article);
+abstract_syntax_tree* taylor_series(
+                                abstract_syntax_tree* ast,
+                                double point,
+                                const char* var,
+                                int pow,
+                                article_builder* article);
 
 #endif

### 2022-12-04 src/main.cpp

@@ -38,7 +38,7 @@ int main()
     abstract_syntax_tree* deriv = derivative(ast, "x", &article);
 
     article_add_section(&article, "Taylor series");
-    abstract_syntax_tree* maclaurin = maclaurin_series(ast, "x", 3, &article);
+    abstract_syntax_tree* taylor = taylor_series(ast, 5, "x", 1, &article);
 
     article_end(&article);
 
@@ -49,10 +49,12 @@ int main()
 
     plot_node(ast->root, stdout);
     putc('\n', stdout);
+    plot_node(taylor->root, stdout);
+    putc('\n', stdout);
 
     tree_dtor(ast);
     tree_dtor(deriv);
-    tree_dtor(maclaurin);
+    tree_dtor(taylor);
     article_dtor(&article);
     return 0;
 }

### 2022-12-05 output/article.tex
feat: add tangent plots

--- 2022-12-04 output/article.tex
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
 \begin{equation}
@@
 
-has a truly wondrous solution, which is sadly too massive to be shown here.
-It can be easily proved, that if we simplify this we wil get
+shall be considered an amusing exercise for the reader.
+Any self-respecting mathematician would find it obvious, that if we simplify this we wil get
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 \end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-We shall ponder the following:
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-Let us take a look at this:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 \end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 \end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 \end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 \end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 \end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 \end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+We are going to study the following:
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 \end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 \end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 \end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 \end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-0 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+0 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 \end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 \end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-We will take a closer look at this:
+The following is worth a closer look:
 \begin{equation}
@@
 \end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
 \begin{equation}
@@
 \end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 \end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 \end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 \end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 \end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 \end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 \end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 \end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 \end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 \end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 \end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 \end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 \end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
 \begin{equation}
@@
 \end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 
-We shall ponder the following:
+Let us take a look at this:
 \begin{equation}
@@
 \end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 
-Consider the following:
+We will take a closer look at this:
 \begin{equation}
@@
 \end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+We shall ponder the following:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 \end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
 \begin{equation}
@@
 \end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-0 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+0 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 \end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 \end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 \end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 
-Let us take a look at this:
+We will take a closer look at this:
 \begin{equation}
@@
 \end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
+We are going to study the following:
 \begin{equation}
@@
 \end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 \end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 \end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 \end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
 \begin{equation}
@@
 \end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-0 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+0 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 \end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 \end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 \end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 \end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+Let us take a look at this:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
+Consider the following:
 \begin{equation}
@@
 \end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We are going to study the following:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 \end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 \end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 \end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 \end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 \end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 \end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 \end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 \end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 \end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 \end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
 \begin{equation}
@@
 \end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 \end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 \end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 \end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
 \begin{equation}
@@
 \end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 \end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
+We are going to study the following:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+The object of our ultimate interest is the following:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 \end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
 \begin{equation}
@@
 \end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 \end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 \end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 \end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 \end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
 \begin{equation}
@@
 \end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 \end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-0 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+0 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 \end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 \end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 \end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+The following is worth a closer look:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 \end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
+We shall ponder the following:
+\begin{equation}
+1 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 \end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+As you can see, the derivative of this is equal to
 \begin{equation}
@@
 \end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 \end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-0 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+0 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 \end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
 \begin{equation}
@@
 \end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
 \begin{equation}
@@
 
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
 \begin{equation}
@@
 
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+Consider the following:
 \begin{equation}
@@
 
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
 \begin{equation}
@@
 \end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
 \begin{equation}
@@
 
-The following is worth a closer look:
-\begin{equation}
-1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Consider the following:
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
 \begin{equation}
@@
 \end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
 \begin{equation}
@@
 
-We shall ponder the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 \begin{equation}
-B + \left( \left( \arctan 1 \right) ^{-2 } + A \right) \cdot \frac{x ^{2 } }{2 } + \left( G + H \right) \cdot \frac{x ^{3 } }{6 } 
+B + \left( \left( \arctan 1 \right) ^{-2 } + A \right) \cdot \frac{\left( x - 0 \right) ^{2 } }{2 } + \left( G + H \right) \cdot \frac{\left( x - 0 \right) ^{3 } }{6 } 
 \end{equation}
@@
 	\item $A = \left( \arctan 1 \right) ^{-2 } \cdot \left( \ln \arctan 1 - 2 \cdot 0 \right) \cdot \left( \ln \arctan 1 - 2 \cdot 0 \right) - \left( \arctan 1 \right) ^{-2 } \cdot 2 \cdot \frac{0.5 \cdot \arctan 1 }{\left( \arctan 1 \right) ^{2 } } $
-	\item $B = 0 + \left( \arctan 1 \right) ^{-2 } \cdot \frac{x ^{0 } }{1 } + \left( \arctan 1 \right) ^{-2 } \cdot \left( \ln \arctan 1 - 2 \cdot 0 \right) \cdot \frac{x ^{1 } }{1 } $
+	\item $B = 0 + \left( \arctan 1 \right) ^{-2 } \cdot \frac{\left( x - 0 \right) ^{0 } }{1 } + \left( \arctan 1 \right) ^{-2 } \cdot \left( \ln \arctan 1 - 2 \cdot 0 \right) \cdot \frac{\left( x - 0 \right) ^{1 } }{1 } $
 	\item $C = \left( \arctan 1 \right) ^{-2 } \cdot \left( \ln \arctan 1 - 2 \cdot 0 \right) \cdot \left( \ln \arctan 1 - 2 \cdot 0 \right) - \left( \arctan 1 \right) ^{-2 } \cdot 2 \cdot \frac{0.5 \cdot \arctan 1 }{\left( \arctan 1 \right) ^{2 } } $
@@
 
+\newpage
+\section{Tangent}
+Let us find the Taylor series at $x = 5$ of the following function:
+\begin{equation}
+\left( x + 1 \right) ^{\frac{\sin x }{2 } } \cdot \left( \arctan \sqrt {x ^{2 } + 1 } \right) ^{x - 2 } 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x - 2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x + 1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+\sin x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x - 2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x - 2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x + 1 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+\sin x 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x - 2 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+1 - 0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x + 1 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+1 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+\sin x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x + 1 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+4 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+\cos x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+-\sin x \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x + 1 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+1 + 0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+\sin x 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+\cos x \cdot 1 
+\end{equation}
+
+Now the proof that the Taylor series of this function at $x = 5$ is equal to
+\begin{equation}
+0 + 6 ^{\frac{\sin 5 }{2 } } \cdot \left( \arctan \sqrt {26 } \right) ^{3 } \cdot \frac{\left( x - 5 \right) ^{0 } }{1 } + \left( B + 6 ^{\frac{\sin 5 }{2 } } \cdot \left( \arctan \sqrt {26 } \right) ^{3 } \cdot \left( A \right) \right) \cdot \frac{\left( x - 5 \right) ^{1 } }{1 }
+\end{equation}
+Where:
+\begin{itemize}
+	\item $A = \ln \arctan \sqrt {26 } + 3 \cdot \frac{\frac{1 }{1 + \left( \sqrt {26 } \right) ^{2 } } \cdot \frac{1 }{2 \cdot \sqrt {26 } } \cdot 10 }{\arctan \sqrt {26 } } $
+	\item $B = 6 ^{\frac{\sin 5 }{2 } } \cdot \left( \frac{\cos 5 \cdot 2 }{4 } \cdot \ln 6 + \frac{\sin 5 }{2 } \cdot 0.166667 \right) \cdot \left( \arctan \sqrt {26 } \right) ^{3 } $
+\end{itemize}
+
+is too trivial to be shown here.
+As you can see, if we simplify this we wil get
+\begin{equation}
+6 ^{\frac{\sin 5 }{2 } } \cdot \left( \arctan \sqrt {26 } \right) ^{3 } + \left( B + 6 ^{\frac{\sin 5 }{2 } } \cdot \left( \arctan \sqrt {26 } \right) ^{3 } \cdot \left( A \right) \right) \cdot \left( x - 5 \right)
+\end{equation}
+Where:
+\begin{itemize}
+	\item $A = \ln \arctan \sqrt {26 } + 3 \cdot \frac{\frac{1 }{1 + \left( \sqrt {26 } \right) ^{2 } } \cdot \frac{1 }{2 \cdot \sqrt {26 } } \cdot 10 }{\arctan \sqrt {26 } } $
+	\item $B = 6 ^{\frac{\sin 5 }{2 } } \cdot \left( \frac{\cos 5 \cdot 2 }{4 } \cdot \ln 6 + \frac{\sin 5 }{2 } \cdot 0.166667 \right) \cdot \left( \arctan \sqrt {26 } \right) ^{3 } $
+\end{itemize}
+
+\includegraphics{"plot.png"}
 \end{document}

### 2022-12-05 lib/parser/ast.cpp

@@ -220,6 +220,23 @@ void plot_node(const ast_node *node, FILE *output)
     #undef PLOT_COMPOUND
 }
 
+void plot_tangent(const ast_node *node, const ast_node* tangent, const char *filename)
+{
+    FILE* plot = popen("gnuplot", "w");
+
+    fputs("set terminal png\n", plot);
+    fprintf(plot, "set output \"%s\"\n", filename);
+    fputs("set grid\n", plot);
+
+    fputs("plot ", plot);
+    plot_node(node, plot);
+    fputs(" title \"y = f(x)\", ", plot);
+    plot_node(tangent, plot);
+    fputs(" title \"tangent\"\n", plot);
+
+    pclose(plot);
+}
+
 static const int MAX_LABELS = 'Z'-'A'+1;
 
 

### 2022-12-05 lib/parser/ast.h

@@ -249,4 +249,6 @@ void print_node(const ast_node* node, string_builder* builder);
  */
 void plot_node(const ast_node* node, FILE* output);
 
+void plot_tangent(const ast_node* func, const ast_node* tangent, const char* filename);
+
 #endif

### 2022-12-05 src/main.cpp

@@ -21,7 +21,6 @@ int main()
 
 
     dynamic_array(token)* tokens = parse_tokens("(x + 1)^{\\frac{\\sin x}{2}} \\cdot (\\arctan \\sqrt{x^2 + 1})^{x - 2}");
-    // dynamic_array(token)* tokens = parse_tokens("\\frac{1}{x + 1}");
     abstract_syntax_tree* ast = build_tree(tokens);
 
     article_builder article = {};
@@ -38,23 +37,23 @@ int main()
     abstract_syntax_tree* deriv = derivative(ast, "x", &article);
 
     article_add_section(&article, "Taylor series");
-    abstract_syntax_tree* taylor = taylor_series(ast, 5, "x", 1, &article);
+    abstract_syntax_tree* taylor = taylor_series(ast, 0, "x", 3, &article);
+
+    article_add_section(&article, "Tangent");
+    abstract_syntax_tree* tangent = taylor_series(ast, 5, "x", 1, &article);
+
+    plot_tangent(ast->root, tangent->root, "output/plot.png");
+    string_builder_append(&article.text, "\\includegraphics{\"plot.png\"}\n");
 
     article_end(&article);
 
     article_build(&article, "output");
 
-    array_dtor(tokens);
-    free(tokens);
-
-    plot_node(ast->root, stdout);
-    putc('\n', stdout);
-    plot_node(taylor->root, stdout);
-    putc('\n', stdout);
-
+    array_dtor(tokens); free(tokens);
     tree_dtor(ast);
     tree_dtor(deriv);
     tree_dtor(taylor);
+    tree_dtor(tangent);
     article_dtor(&article);
     return 0;
 }

### 2022-12-13 output/article.tex
feat: input file

--- 2022-12-04 output/article.tex
@@
 \begin{equation}
-\left( x + 1 \right) ^{\frac{\sin x }{2 } } \cdot \left( \arctan \sqrt {x ^{2 } + 1 } \right) ^{x - 2 } 
+\sin x ^{3 } + \left( \cos 15 \cdot x \right) ^{4 } 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{3 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+3 \cdot x ^{3 - 1 } \cdot 1 
+\end{equation}
+
+Now the proof that the derivative of this function is equal to
+\begin{equation}
+\cos x ^{3 } \cdot 3 \cdot x ^{3 - 1 } \cdot 1 + 4 \cdot \left( \cos 15 \cdot x \right) ^{4 - 1 } \cdot -\sin 15 \cdot x \cdot \left( 0 \cdot x + 15 \cdot 1 \right) 
+\end{equation}
+shall be considered an amusing exercise for the reader.
+Unsurprisingly, if we simplify this we wil get
+\begin{equation}
+\cos x ^{3 } \cdot 3 \cdot x ^{2 } - 4 \cdot \left( \cos 15 \cdot x \right) ^{3 } \cdot \sin 15 \cdot x \cdot 15 
+\end{equation}
+\newpage
+\section{Taylor series}
+Let us find the Taylor series at $x = 0$ of the following function:
+\begin{equation}
+\sin x ^{3 } + \left( \cos 15 \cdot x \right) ^{4 } 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{3 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+3 \cdot x ^{3 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+15 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+4 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
 \end{equation}
@@
 \begin{equation}
-1 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
+3 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{3 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+3 \cdot x ^{3 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+15 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+15 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+3 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+4 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+15 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+15 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+4 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
 \begin{equation}
@@
 \begin{equation}
-x - 2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-1 - 0 
+3 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+3 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{3 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+3 \cdot x ^{3 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+3 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{3 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+3 \cdot x ^{3 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+15 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+15 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+15 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+3 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+4 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+15 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+15 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+15 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
 \end{equation}
@@
 \begin{equation}
-x + 1 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-Let us take a look at this:
+3 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+15 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+15 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+3 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+4 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+15 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+15 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+15 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+4 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+15 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+15 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+15 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+3 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+4 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+3 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+3 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{3 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+3 \cdot x ^{3 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+3 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+3 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{3 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+3 \cdot x ^{3 - 1 } \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+3 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+3 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{3 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+3 \cdot x ^{3 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+3 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+3 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{3 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+3 \cdot x ^{3 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+6 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{3 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+3 \cdot x ^{3 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+6 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+3 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{3 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+3 \cdot x ^{3 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+3 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+3 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+x ^{3 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+3 \cdot x ^{3 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+3 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+3 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{3 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+3 \cdot x ^{3 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+3 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+3 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{3 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+3 \cdot x ^{3 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+3 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+3 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{3 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+3 \cdot x ^{3 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+3 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+6 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{3 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+3 \cdot x ^{3 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+3 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+3 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{3 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+3 \cdot x ^{3 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+3 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+3 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{3 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+3 \cdot x ^{3 - 1 } \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+3 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+3 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+3 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{3 } 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+3 \cdot x ^{3 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+3 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{3 } 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+3 \cdot x ^{3 - 1 } \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+6 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+3 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+x ^{3 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+3 \cdot x ^{3 - 1 } \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+3 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 \cdot x 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 2 \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+3 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+x ^{3 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+3 \cdot x ^{3 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+3 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+3 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+x ^{3 } 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+3 \cdot x ^{3 - 1 } \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+6 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+3 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{3 } 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+3 \cdot x ^{3 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+15 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+15 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+15 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+15 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+3 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+4 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+15 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+15 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+15 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+15 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+We are going to study the following:
 \begin{equation}
@@
 \end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-\sin x 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-Now the proof that the derivative of this function is equal to
-\begin{equation}
-\left( x + 1 \right) ^{\frac{\sin x }{2 } } \cdot \left( A \right) \cdot \left( \arctan \sqrt {x ^{2 } + 1 } \right) ^{x - 2 } + \left( x + 1 \right) ^{\frac{\sin x }{2 } } \cdot \left( \arctan \sqrt {x ^{2 } + 1 } \right) ^{x - 2 } \cdot \left( C \right)
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+3 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+15 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+15 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+3 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+4 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+15 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+15 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+15 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+15 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+2 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+3 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+15 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+15 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+15 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+2 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+15 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+15 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+2 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+3 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+15 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+15 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+15 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+3 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+15 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+15 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+15 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+2 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+3 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+4 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+15 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+15 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+15 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+15 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+3 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+15 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+15 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+3 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+4 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+15 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+15 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+15 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+15 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+3 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+4 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+15 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+15 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+15 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+15 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+4 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+15 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+15 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+15 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+One shall regard the object in question with utmost interest:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+15 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+3 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+4 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+15 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+15 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+The following is worth a closer look:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+15 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+15 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+2 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Let us take a look at this:
+\begin{equation}
+3 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+15 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+15 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Clearly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+3 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Consider the following:
+\begin{equation}
+4 
+\end{equation}
+As you can see, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+Now the proof that the Taylor series of this function at $x = 0$ is equal to
+\begin{equation}
+A + 6 \cdot \frac{\left( x - 0 \right) ^{3 } }{6 } + 2.025e+06 \cdot \frac{\left( x - 0 \right) ^{4 } }{24 } 
 \end{equation}
@@
 \begin{itemize}
-	\item $A = \frac{\cos x \cdot 1 \cdot 2 - \sin x \cdot 0 }{2 ^{2 } } \cdot \ln \left( x + 1 \right) + \frac{\sin x }{2 } \cdot \frac{1 + 0 }{x + 1 } $
-	\item $B = \frac{1 }{1 + \left( \sqrt {x ^{2 } + 1 } \right) ^{2 } } \cdot \frac{1 }{2 \cdot \sqrt {x ^{2 } + 1 } } \cdot \left( 2 \cdot x ^{2 - 1 } \cdot 1 + 0 \right) $
-	\item $C = \left( 1 - 0 \right) \cdot \ln \arctan \sqrt {x ^{2 } + 1 } + \left( x - 2 \right) \cdot \frac{B }{\arctan \sqrt {x ^{2 } + 1 } } $
+	\item $A = 0 + 1 \cdot \frac{\left( x - 0 \right) ^{0 } }{1 } + 0 \cdot \frac{\left( x - 0 \right) ^{1 } }{1 } + -900 \cdot \frac{\left( x - 0 \right) ^{2 } }{2 } $
 \end{itemize}
 
-has a truly wondrous solution, which is sadly too massive to be shown here.
-It can be easily proved, that if we simplify this we wil get
-\begin{equation}
-A \cdot \left( \arctan \sqrt {x ^{2 } + 1 } \right) ^{x - 2 } + \left( x + 1 \right) ^{\frac{\sin x }{2 } } \cdot C 
-\end{equation}
-Where:
-\begin{itemize}
-	\item $A = \left( x + 1 \right) ^{\frac{\sin x }{2 } } \cdot \left( \frac{\cos x \cdot 2 }{4 } \cdot \ln \left( x + 1 \right) + \frac{\sin x }{2 } \cdot \frac{1 }{x + 1 } \right) $
-	\item $B = \frac{1 }{1 + \left( \sqrt {x ^{2 } + 1 } \right) ^{2 } } \cdot \frac{1 }{2 \cdot \sqrt {x ^{2 } + 1 } } \cdot 2 \cdot x $
-	\item $C = \left( \arctan \sqrt {x ^{2 } + 1 } \right) ^{x - 2 } \cdot \left( \ln \arctan \sqrt {x ^{2 } + 1 } + \left( x - 2 \right) \cdot \frac{B }{\arctan \sqrt {x ^{2 } + 1 } } \right) $
-\end{itemize}
-
+shall be considered an amusing exercise for the reader.
+It is now obvious, that if we simplify this we wil get
+\begin{equation}
+1 - 900 \cdot \frac{x ^{2 } }{2 } + 6 \cdot \frac{x ^{3 } }{6 } + 2.025e+06 \cdot \frac{x ^{4 } }{24 } 
+\end{equation}
 \newpage
-\section{Taylor series}
-Let us find the Taylor series at $x = 5$ of the following function:
-\begin{equation}
-\left( x + 1 \right) ^{\frac{\sin x }{2 } } \cdot \left( \arctan \sqrt {x ^{2 } + 1 } \right) ^{x - 2 } 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
+\section{Tangent}
+Let us find the Taylor series at $x = 0$ of the following function:
+\begin{equation}
+\sin x ^{3 } + \left( \cos 15 \cdot x \right) ^{4 } 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+x ^{3 } 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+3 \cdot x ^{3 - 1 } \cdot 1 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+15 
+\end{equation}
+Obviously, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+It can be easily proved, that the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+15 \cdot x 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+0 \cdot x + 15 \cdot 1 
+\end{equation}
+
+The object of our ultimate interest is the following:
+\begin{equation}
+4 
+\end{equation}
+Trivially, the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We will take a closer look at this:
+\begin{equation}
+x ^{2 } 
+\end{equation}
+Unsurprisingly, the derivative of this is equal to
+\begin{equation}
+2 \cdot x ^{2 - 1 } \cdot 1 
+\end{equation}
+
+We are going to study the following:
+\begin{equation}
+3 
+\end{equation}
+It is now obvious, that the derivative of this is equal to
+\begin{equation}
+0 
+\end{equation}
+
+We shall ponder the following:
+\begin{equation}
+x ^{3 } 
+\end{equation}
+Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
+\begin{equation}
+3 \cdot x ^{3 - 1 } \cdot 1 
+\end{equation}
+
+Now the proof that the Taylor series of this function at $x = 0$ is equal to
+\begin{equation}
+0 + 1 \cdot \frac{\left( x - 0 \right) ^{0 } }{1 } + 0 \cdot \frac{\left( x - 0 \right) ^{1 } }{1 } 
+\end{equation}
+is left out for the reader to solve themselves.
+Any self-respecting mathematician would find it obvious, that if we simplify this we wil get
 \begin{equation}
@@
 \end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x - 2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-x + 1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-\sin x 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-2 \cdot x 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 \cdot x + 2 \cdot 1 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-2 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-1 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x - 2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
-\begin{equation}
-1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x - 2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-x + 1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-Unsurprisingly, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-\sin x 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-1 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-x ^{2 } 
-\end{equation}
-Obviously, the derivative of this is equal to
-\begin{equation}
-2 \cdot x ^{2 - 1 } \cdot 1 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x - 2 
-\end{equation}
-As you can see, the derivative of this is equal to
-\begin{equation}
-1 - 0 
-\end{equation}
-
-Consider the following:
-\begin{equation}
-x + 1 
-\end{equation}
-Clearly, the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-1 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We are going to study the following:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We shall ponder the following:
-\begin{equation}
-\sin x 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-x + 1 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-The object of our ultimate interest is the following:
-\begin{equation}
-4 
-\end{equation}
-Trivially, the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-We will take a closer look at this:
-\begin{equation}
-2 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-\cos x 
-\end{equation}
-Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
-\begin{equation}
--\sin x \cdot 1 
-\end{equation}
-
-One shall regard the object in question with utmost interest:
-\begin{equation}
-x + 1 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-1 + 0 
-\end{equation}
-
-Let us take a look at this:
-\begin{equation}
-2 
-\end{equation}
-It is now obvious, that the derivative of this is equal to
-\begin{equation}
-0 
-\end{equation}
-
-The following is worth a closer look:
-\begin{equation}
-\sin x 
-\end{equation}
-It can be easily proved, that the derivative of this is equal to
-\begin{equation}
-\cos x \cdot 1 
-\end{equation}
-
-Now the proof that the Taylor series of this function at $x = 5$ is equal to
-\begin{equation}
-0 + 6 ^{\frac{\sin 5 }{2 } } \cdot \left( \arctan \sqrt {26 } \right) ^{3 } \cdot \frac{\left( x - 5 \right) ^{0 } }{1 } + \left( B + 6 ^{\frac{\sin 5 }{2 } } \cdot \left( \arctan \sqrt {26 } \right) ^{3 } \cdot \left( A \right) \right) \cdot \frac{\left( x - 5 \right) ^{1 } }{1 }
-\end{equation}
-Where:
-\begin{itemize}
-	\item $A = \ln \arctan \sqrt {26 } + 3 \cdot \frac{\frac{1 }{1 + \left( \sqrt {26 } \right) ^{2 } } \cdot \frac{1 }{2 \cdot \sqrt {26 } } \cdot 10 }{\arctan \sqrt {26 } } $
-	\item $B = 6 ^{\frac{\sin 5 }{2 } } \cdot \left( \frac{\cos 5 \cdot 2 }{4 } \cdot \ln 6 + \frac{\sin 5 }{2 } \cdot 0.166667 \right) \cdot \left( \arctan \sqrt {26 } \right) ^{3 } $
-\end{itemize}
-
-is too trivial to be shown here.
-It is now obvious, that if we simplify this we wil get
-\begin{equation}
-6 ^{\frac{\sin 5 }{2 } } \cdot \left( \arctan \sqrt {26 } \right) ^{3 } + \left( B + 6 ^{\frac{\sin 5 }{2 } } \cdot \left( \arctan \sqrt {26 } \right) ^{3 } \cdot \left( A \right) \right) \cdot \left( x - 5 \right)
-\end{equation}
-Where:
-\begin{itemize}
-	\item $A = \ln \arctan \sqrt {26 } + 3 \cdot \frac{\frac{1 }{1 + \left( \sqrt {26 } \right) ^{2 } } \cdot \frac{1 }{2 \cdot \sqrt {26 } } \cdot 10 }{\arctan \sqrt {26 } } $
-	\item $B = 6 ^{\frac{\sin 5 }{2 } } \cdot \left( \frac{\cos 5 \cdot 2 }{4 } \cdot \ln 6 + \frac{\sin 5 }{2 } \cdot 0.166667 \right) \cdot \left( \arctan \sqrt {26 } \right) ^{3 } $
-\end{itemize}
-
+\includegraphics{"plot.png"}
 \end{document}

### 2022-12-13 lib/dynamic_array/_array_macros.h

@@ -9,19 +9,19 @@ struct dynamic_array_##type \
 }
 
 #define DEFINE_ARRAY_CTOR(type) \
-void array_ctor(dynamic_array(type)* array)
+    void array_ctor(dynamic_array(type)* array)
 
 #define DEFINE_ARRAY_DTOR(type) \
-void array_dtor(dynamic_array(type)* array)
+    void array_dtor(dynamic_array(type)* array)
 
 #define DEFINE_ARRAY_PUSH(type) \
-void array_push(dynamic_array(type)* array, type element)
+    void array_push(dynamic_array(type)* array, type element)
 
 #define DEFINE_ARRAY_POP(type) \
-void array_pop(dynamic_array(type)* array)
+    void array_pop(dynamic_array(type)* array)
 
 #define DEFINE_ARRAY_COPY(type) \
-void array_copy(dynamic_array(type)* dest, const dynamic_array(type)* src)
+    void array_copy(dynamic_array(type)* dest, const dynamic_array(type)* src)
 
 #define DEFINE_ARRAY_GET(type) \
-type* array_get_element(const dynamic_array(type)* array, size_t index)
+    type* array_get_element(const dynamic_array(type)* array, size_t index)

### 2022-12-13 lib/parser/ast.cpp

@@ -220,16 +220,22 @@ void plot_node(const ast_node *node, FILE *output)
     #undef PLOT_COMPOUND
 }
 
-void plot_tangent(const ast_node *node, const ast_node* tangent, const char *filename)
+void plot_tangent(const ast_node* func,
+                    const ast_node* tangent,
+                    const char* filename,
+                    double range_left,
+                    double range_right)
 {
     FILE* plot = popen("gnuplot", "w");
 
     fputs("set terminal png\n", plot);
     fprintf(plot, "set output \"%s\"\n", filename);
     fputs("set grid\n", plot);
+    fprintf(plot, "set xrange [%lg:%lg]\n", range_left, range_right);
+    fputs("set samples 400\n", plot);
 
     fputs("plot ", plot);
-    plot_node(node, plot);
+    plot_node(func, plot);
     fputs(" title \"y = f(x)\", ", plot);
     plot_node(tangent, plot);
     fputs(" title \"tangent\"\n", plot);

### 2022-12-13 lib/parser/ast.h

@@ -249,6 +249,10 @@ void print_node(const ast_node* node, string_builder* builder);
  */
 void plot_node(const ast_node* node, FILE* output);
 
-void plot_tangent(const ast_node* func, const ast_node* tangent, const char* filename);
+void plot_tangent(const ast_node* func,
+                    const ast_node* tangent,
+                    const char* filename,
+                    double range_left = -10,
+                    double range_right = 10);
 
 #endif

### 2022-12-13 src/diff_utils.cpp

@@ -1,0 +1,67 @@
+#include <stdio.h>
+#include <string.h>
+
+#include "logger.h"
+
+#include "diff_utils.h"
+
+int prog_init(prog_state *state, const char *filename)
+{
+    FILE* input = fopen(filename, "r");
+    LOG_ASSERT_ERROR(input != NULL, return -1, "File not found '%s'", filename);
+
+    LOG_ASSERT_ERROR(
+        fscanf(input, " $f(%m[^)]) = %m[^$]$", &state->var_name, &state->function) == 2,
+        return -1,
+        "Corrupted input file '%s': invalid function", filename
+    );
+    char* read_var = NULL;
+    LOG_ASSERT_ERROR(
+        fscanf(input, " Taylor series at %lg to $%m[^^]^%d$",
+            &state->taylor_at,
+            &read_var,
+            &state->taylor_pow) == 3,
+        return -1,
+        "Corrupted input file '%s': invalid Taylor series", filename
+    );
+    LOG_ASSERT_ERROR(
+        strcmp(read_var, state->var_name) == 0,
+        {free(read_var); return -1;},
+        "Corrupted input file '%s': function variable '%s' does not match with Taylor series variable '%s'",
+        filename, state->var_name, read_var
+    );
+    free(read_var);
+    LOG_ASSERT_ERROR(
+        fscanf(input, " Tangent at $%m[^=]=%lg$", &read_var, &state->tangent_at) == 2,
+        return -1,
+        "Corrupted input file '%s': invalid tangent", filename
+    );
+    LOG_ASSERT_ERROR(
+        strcmp(read_var, state->var_name) == 0,
+        {free(read_var); return -1;},
+        "Corrupted input file '%s': function variable '%s' does not match with tangent variable '%s'",
+        filename, state->var_name, read_var
+    );
+    free(read_var);
+    LOG_ASSERT_ERROR(
+        fscanf(input, " Plot in range [%lg, %lg]", &state->range_start, &state->range_end) == 2,
+        return -1,
+        "Corrupted input file '%s': invalid range",
+        filename
+    );
+    LOG_ASSERT_ERROR(
+        state->range_start < state->range_end,
+        return -1,
+        "Corrupted input file '%s': invalid range boundaries",
+        filename
+    );
+    fclose(input);
+    return 0;
+}
+
+void prog_state_dtor(prog_state *state)
+{
+    free(state->function);
+    free(state->var_name);
+    memset(state, 0, sizeof(*state));
+}

### 2022-12-13 src/diff_utils.h

@@ -1,0 +1,18 @@
+#ifndef DIFF_UTILS_H
+#define DIFF_UTILS_H
+
+struct prog_state
+{
+    char* function;
+    char* var_name;
+    double taylor_at;
+    int taylor_pow;
+    double tangent_at;
+    double range_start;
+    double range_end;
+};
+
+int prog_init(prog_state* state, const char* filename);
+void prog_state_dtor(prog_state* state);
+
+#endif

### 2022-12-13 src/main.cpp

@@ -9,7 +9,9 @@
 #include "tree_math.h"
 #include "article_builder.h"
 
-int main()
+#include "diff_utils.h"
+
+int main(int argc, const char** argv)
 {
     add_default_file_logger();
     add_logger({
@@ -19,9 +21,18 @@ int main()
         .settings_mask = LGS_KEEP_OPEN | LGS_USE_ESCAPE
     }); // TODO: can this be in default logger?
 
+    prog_state state = {};
+    const char* filename = argc > 1 
+                            ? argv[1]
+                            : "Funcfile";
 
-    dynamic_array(token)* tokens = parse_tokens("(x + 1)^{\\frac{\\sin x}{2}} \\cdot (\\arctan \\sqrt{x^2 + 1})^{x - 2}");
+    LOG_ASSERT(prog_init(&state, filename) == 0, {prog_state_dtor(&state); return 1;});
+
+    dynamic_array(token)* tokens = parse_tokens(state.function);
+    LOG_ASSERT(tokens != NULL, {prog_state_dtor(&state); return 1;});
     abstract_syntax_tree* ast = build_tree(tokens);
+    array_dtor(tokens); free(tokens);
+    LOG_ASSERT(ast != NULL, {prog_state_dtor(&state); return 1;});
 
     article_builder article = {};
     article_ctor(&article);
@@ -34,26 +45,26 @@ int main()
     article_add_abstract(&article, "Wonderful article");
 
     article_add_section(&article, "Derivative");
-    abstract_syntax_tree* deriv = derivative(ast, "x", &article);
+    abstract_syntax_tree* deriv = derivative(ast, state.var_name, &article);
 
     article_add_section(&article, "Taylor series");
-    abstract_syntax_tree* taylor = taylor_series(ast, 0, "x", 3, &article);
+    abstract_syntax_tree* taylor = taylor_series(ast, state.taylor_at, state.var_name, state.taylor_pow, &article);
 
     article_add_section(&article, "Tangent");
-    abstract_syntax_tree* tangent = taylor_series(ast, 5, "x", 1, &article);
+    abstract_syntax_tree* tangent = taylor_series(ast, state.tangent_at, state.var_name, 1, &article);
 
-    plot_tangent(ast->root, tangent->root, "output/plot.png");
+    plot_tangent(ast->root, tangent->root, "output/plot.png", state.range_start, state.range_end);
[…]
